---
output: github_document
bibliography: sure_bib.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Reproduce Results of @gerard2015adaptive
This folder contains the code necessary to reproduce the results of @gerard2015adaptive. To reproduce these results you will need to:

1. Download the appropriate R packages.
2. Run `make`.
3. Get some coffee.

# Download the appropriate R packages.
You can obtain all of the needed R packages by running the following code in R:
```{r, eval = FALSE}
install.packages(c("dplyr", "ggplot2", "tidyr", "xtable", 
                   "devtools", "snow", "cate", "ggthemes",
                   "stringr"))
source("https://bioconductor.org/biocLite.R")
biocLite("sva")
devtools::install_github("dcgerard/tensr")
devtools::install_github("dcgerard/hose")
```

To download the code in this repo, click on [this link](https://github.com/dcgerard/hose_paper/archive/master.zip).

# Run `make`
To reproduce all of the results of @gerard2015adaptive, simply run `make` from the terminal (not in the R session). To reproduce the figure from Section 2, run in the terminal:
``` shell
make change_sv
```

To reproduce the simulation results from the paper, run in the terminal:
``` shell
make sims
```

To reproduce the analysis of NBA statistics, run in the terminal:
``` shell
make nba
```

# Get coffee
Some of the simulations will take awhile to run (2 to 10 hours depending on how many cores you are using). You should get some coffee! Here is a list of some of my favorite places:

* Chicago
    - [Sawada Coffee](https://www.yelp.com/biz/sawada-coffee-chicago)
    - [Plein Air Cafe](https://www.yelp.com/biz/plein-air-cafe-and-eatery-chicago-2)
* Seattle
    - [Bauhaus Ballard](https://www.yelp.com/biz/bauhaus-ballard-seattle)
    - [Cafe Solstice](https://www.yelp.com/biz/cafe-solstice-seattle)
* Columbus
    - [Yeah, Me Too](https://www.yelp.com/biz/yeah-me-too-columbus)
    - [Stauf's Coffee Roasters](https://www.yelp.com/biz/staufs-coffee-roasters-columbus-2)
    - [Caffe Apropos](https://www.yelp.com/biz/caff%C3%A9-apropos-columbus-2)


# Bugs
If you have trouble running this code, then it might be that you need to update your R packages. I ran these simulations under these settings:
```{r, echo = FALSE, message=FALSE}
library(dplyr)
library(hose)
library(tensr)
library(ggplot2)  
library(tidyr)
library(xtable)
library(snow)
library(sva)
library(cate)
library(ggthemes)
library(stringr)
```

```{r}
sessionInfo()
```

As you can see above, I've only tried this on Linux. 

If you still have difficulty, please submit an [issue](https://github.com/dcgerard/reproduce_sure/issues).

# References
